Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-16 report/report.tex
Update todo
Fix citings

\usepackage{csquotes} % Recommended by biblatex
\usepackage[style=numeric,sorting=none,backend=biber]{biblatex}
\addbibresource{references.bib} % The file containing our references, in BibTeX format

@@

The next notable study to assess the quality of OSM data was published by (Kunze, 2012). The study applied different methods to assess the completeness of OSM data in two federal states in Germany, mainly by analysing the area difference between the OSM dataset and an administrative dataset. Finally, a notable study in 2013-2014, conducted by researchers from various universities in Norway and Germany (Fan et al, 2014), examined the quality and accuracy in building footprint data of the Munich area, at a time and place where the completeness of the OSM dataset was significantly higher (the results of their study showed that the OSM had captured close to 100\% of all building footprints). At the time Munich was one of the most developed cities in OSM. Their study included an insight in the geometrical calculations neccessary to match features and points between two datasets, and how to reliably calculate the metrics needed for the most important and assessible of van Oorts criteria. Their study revealed that although the feature completeness of OSM was high, some architectural details were missing. The results reveal that the positional accuracy of OSM data at the time was about 4 meters.

@@

The OSM project is a wiki-like geodatabase based on Volunteered Geographical Information (VGI), meaning anyone can contribute by adding or editing features.
OSM road data and building footprints are commonly obtained by manually tracing features in commercially available satellite images.
Such images have a limit on their resolution which puts a theoretical limit on the accuracy of map features compared to their real-world equivalents (Haklay 2010).
Particularily the high resolution imagery from Bing in 2010 led to an increase in building information in OSM, and the positional error is largely due to the limited resolution in such satellite imagery. (Fan et al, 2014).

@@

(Fan et al., 2014) used the fraction of the total building area in their reference dataset and the OSM dataset to assess the completeness of OSM data.
The motivation for this is to eliminate semantic differences between both datasets.
A very common example of a semantic error when comparing geographic data is that a large building in one dataset may be segmented into several smaller ones in the other, that is to say a building in one set is represented as an aggreation of mutliple buildings in the other set.
This makes a complete one-to-one object mapping impossible.
Rather, buildings have to be identified as 1:1 (one to one), 1:n (one to many) or 1:0 (one to none) cases, depending on if a building is fully represented in the other dataset, represented as an aggregation of smaller plots, or not found at all.
Figure \ref{fig:building-match-types} shows examples of two buildings that were found in the OSM and SLU datasets as 1:1 and 1:n matches respectively.

@@

The final problem is that even when building polygons have been matched between the two datasets, they may not have one-to-one vertex relationship.
Footprints from different datasets may be formed at a different level of detail.
Problems that arise are e.g. that the vertex counts are dissimilar, or that vertex clusters may be found at different parts of the polygon in the two datasets.
To avoid this effect, key points are extracted using the Douglas-Peucker algorithm \cite{douglas-73}, to create a simplifed footprint with less points that still retain information about the rough features of the detailed footprint.
The idea behind Douglas-Peucker is to recursively divide a polyline.
It initially marks only the start and end points $(v_0, v_n)$ to be kept, and finds the point $v_i$ in between whose distance is the greatest to the line segment between $v_0$ and $v_n$.
It then recursively refines the line segments $(v_0, v_i)$ and $(v_i, v_n)$, and proceeds to do so until a line segment $(v_j, v_k)$ is found, where every point in between $v_j$ and $v_k$ have a distance to the line segment $(v_j, v_k)$ that is smaller than some resolution $\epsilon$.
Then $v_j$ are added to the simplified polyline, and all nodes in between them are discarded.
See Algorithm 1 for a detailed view.
In either case The Oriented Minimum Bounding Rectangle (OMBR) is calculated for the two polygons.
Finally the OMBR for the OSM building footprint is shifted so that its centroid aligns with the centroid of the OMBR of the SLU building footprint.
Any edges in the simplified footprints that coinside with the OMBR from the same dataset are extracted, and the corresponding points in the original footprints will be matched with each other.

@@

% Scietific study
% TODO: Find papers and topics for the scientific study (Building footprints, building heights, LOD levels)
% TODO: Read through Todor's recommended papers
% TODO: Scientific study, show how my work integrates in the 3D city reconstruction process.
    % TODO: A lot of the metrics I've used applyg for building accuracy as well (Fan)
    % TODO: Scientific study: Potential application: A method of generating cities on the cheap
% TODO: Scientific study: A set of recommendations.

>>>>

%\usepackage{csquotes} % Recommended by biblatex
\usepackage[style=numeric,sorting=none,backend=biber,citestyle=verbose]{biblatex}
%\addbibresource{references.bib} % The file containing our references, in BibTeX format

@@

The next notable study to assess the quality of OSM data was published by (Kunze, 2012). The study applied different methods to assess the completeness of OSM data in two federal states in Germany, mainly by analysing the area difference between the OSM dataset and an administrative dataset. Finally, a notable study in 2013-2014, conducted by researchers from various universities in Norway and Germany \textbf{(Fan et al, 2014)}, examined the quality and accuracy in building footprint data of the Munich area, at a time and place where the completeness of the OSM dataset was significantly higher (the results of their study showed that the OSM had captured close to 100\% of all building footprints). At the time Munich was one of the most developed cities in OSM. Their study included an insight in the geometrical calculations neccessary to match features and points between two datasets, and how to reliably calculate the metrics needed for the most important and assessible of van Oorts criteria. Their study revealed that although the feature completeness of OSM was high, some architectural details were missing. The results reveal that the positional accuracy of OSM data at the time was about 4 meters.

@@

The OSM project is a wiki-like geodatabase based on Volunteered Geographical Information (VGI), meaning anyone can contribute by adding or editing features.
OSM road data and building footprints are commonly obtained by manually tracing features in commercially available satellite images.
Such images have a limit on their resolution which puts a theoretical limit on the accuracy of map features compared to their real-world equivalents (Haklay 2010).
Particularily the high resolution imagery from Bing in 2010 led to an increase in building information in OSM, and the positional error is largely due to the limited resolution in such satellite imagery. \textbf{(Fan et al, 2014)}.

@@

\textbf{(Fan et al, 2014)} used the fraction of the total building area in their reference dataset and the OSM dataset to assess the completeness of OSM data.
The motivation for this is to eliminate semantic differences between both datasets.
A very common example of a semantic error when comparing geographic data is that a large building in one dataset may be segmented into several smaller ones in the other, that is to say a building in one set is represented as an aggreation of mutliple buildings in the other set.
This makes a complete one-to-one object mapping impossible.
Rather, buildings have to be identified as 1:1 (one to one), 1:n (one to many) or 1:0 (one to none) cases, depending on if a building is fully represented in the other dataset, represented as an aggregation of smaller plots, or not found at all.
Figure \ref{fig:building-match-types} shows examples of two buildings that were found in the OSM and SLU datasets as 1:1 and 1:n matches respectively.

@@

The final problem is that even when building polygons have been matched between the two datasets, they may not have one-to-one vertex relationship.
Footprints from different datasets may be formed at a different level of detail.
Problems that arise are e.g. that the vertex counts are dissimilar, or that vertex clusters may be found at different parts of the polygon in the two datasets.
To avoid this effect, key points are extracted using the Douglas-Peucker algorithm \textbf{(Douglas and Peucker, 1973)}, to create a simplifed footprint with less points that still retain information about the rough features of the detailed footprint.
The idea behind Douglas-Peucker is to recursively divide a polyline.
It initially marks only the start and end points $(v_0, v_n)$ to be kept, and finds the point $v_i$ in between whose distance is the greatest to the line segment between $v_0$ and $v_n$.
It then recursively refines the line segments $(v_0, v_i)$ and $(v_i, v_n)$, and proceeds to do so until a line segment $(v_j, v_k)$ is found, where every point in between $v_j$ and $v_k$ have a distance to the line segment $(v_j, v_k)$ that is smaller than some resolution $\epsilon$.
Then $v_j$ are added to the simplified polyline, and all nodes in between them are discarded.
See Algorithm 1 for a detailed view.
In either case The Oriented Minimum Bounding Rectangle (OMBR) is calculated for the two polygons.
Finally the OMBR for the OSM building footprint is shifted so that its centroid aligns with the centroid of the OMBR of the SLU building footprint.
Any edges in the simplified footprints that coinside with the OMBR from the same dataset are extracted, and the corresponding points in the original footprints will be matched with each other.

@@

% Scietific study
% TODO: Find papers and topics for the scientific study (Building footprints, building heights, LOD levels)
% TODO: Scientific study, show how my work integrates in the 3D city reconstruction process.
    % TODO: Scientific study: Potential application: A method of generating cities on the cheap
% TODO: Scientific study: A set of recommendations.
